%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteer Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Document Archiver} % Job title
    {Vernon Family Doctor's Clinic} % Organization
    {Vernon, BC} % Location
    {July 2014 - August 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I archived hundreds of old, water-damaged patient records. This involved scanning (and sometimes reassembling) the documents into a computer, extracting the patients demographics, and sorting into the correct folder on the archival hard drive.}
        \item {I was also responsible for maintaining and fixing the back-up system for the records.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LIT (Leader in Training) 1} % Job title
    {Eagle Bay Camp} % Organization
    {Eagle Bay, BC} % Location
    {August 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{This was the first level of a volunteer leadership-building program at Eagle Bay Camp (a Bible camp).}
        \item{Development of basic leadership skills was core to this program, and it has served me well in every leadership situation since.}
        \item{I learned how to lead a cabin, I helped maintain and clean the camp, and I learned how to teach children about the Bible.}
        \item{One main event was shadowing a paid cabin leader for a week, which taught me many things about childcare and mentorship.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LIT (Leader in Training) 2} % Job title
    {Eagle Bay Camp} % Organization
    {Eagle Bay, BC} % Location
    {July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{This was the second level of Eagle Bay's LIT program.}
        \item{This was a more intense version of LIT 1, wherein I learned more in-depth ways to be a leader.}
        \item{I co-lead a cabin with another LIT for a week, without assistance from the paid staff.}
        \item{I spent a week shadowing one of the non-cabin leader staff members, for a look at the administrative side of running Eagle Bay.}
        \item{I also recieved increased mentorship in the Bible, and assumed more cleaning-related duties.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Route 6 Youth Leader} % Job title
    {Vernon Alliance Church} % Organization
    {Vernon, BC} % Location
    {September 2015 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{I helped lead and teach a group of Grade 6 boys during their first year out of regular Sunday school.}
        \item{Duties included setting up and running group games, supervising and participating in the sermon, preparing snacks, and mentoring my group of boys.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Reign Community Group Leader} % Job title
    {Vernon Alliance Church} % Organization
    {Vernon, BC} % Location
    {September 2016 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{I got to follow the same group of boys I mentored in Route 6 to our church's main youth ministries.}
        \item{I mentored these boys through their 7th and 8th grades.}
        \item{I helped set up and run (much larger) group games, supervise worship and sermons, and mentor my boys for thirty minutes after worship with my co-leaders.}
        \item{I occasionally performed piano with the worship team (and eventually started playing in our main church services too!).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Guatemala Missions Trip} % Job title
    {Food for the Hungry \& Vernon Alliance Church} % Organization
    {Xonca, Quiché, Guatemala} % Location
    {March 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{I helped install reusable, zero-power water filters in the homes of a group of impoverished indegenous peoples, as well as teach them how to use the filters.}
        \item{I also played with the children of the village (\textit{very} often), and taught them stories from the Bible.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Camp Volunteer} % Job title
    {Okanagan Science Centre} % Organization
    {Vernon, BC} % Location
    {July 2016 - August 2016, July 2018 - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{I volunteered for around seven hours every weekday in the OSC's summer camps.}
        \item{This involved assisting in labs, demonstrations and activities, supervising the children during their time in the exhibits and in nearby Polson Park, and cleaning the facility.}
        \item{One of my favourite roles was helping set up and teach about Arduinos and basic circuitry in an electronics camp.}
      \end{cvitems}
    }

\end{cventries}
