%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Piano, clarinet, and voice} % Affiliation/role
    {Music} % Organisation/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {I started playing the piano when I was four years old, and I've never stopped. So far, I have managed to attain my Grade 8 RCM certification for piano, but I have also learned several Grade 9 and 10 level pieces.}
        \item {I started playing clarinet in Kalamalka Secondary's band in grade 8. This led to me joining (and falling in love with) the jazz band. Eventually, I switched to playing piano in the jazz band, but I kept playing clarinet by joining the OSYO in their 2017/18 concert season.}
        \item {I took private voice lessons from 2011-2017, with a focus on show tunes and classical singing. I have performed with my school's choir, as well as in multiple musicals both in and out of school. In 2017, I performed in the main male role of \textit{Emma! A Pop Musical} with my school.}
        \item {Music is an absolutely integral part of my life. I owe everything I am to it.}
      \end{cvitems}
    }

  \cventry
    {Shodan in Meibukan Gōjū-ryū Karate-do}
    {North Star Martial Arts Academy}
    {Vernon, BC}
    {September 2006 - Present}
    {I have been practising Karate since the age of six. After years of perseverance, I earned my first-degree black belt (shodan) in June 2017. Karate has taught me everything I know about perseverance, honesty, and integrity.}

  \cventry
    {Programmer on the ECE Team}
    {Space Exploration Alberta Robotics (SPEAR)}
    {University of Alberta, Edmonton, AB}
    {September 2018 - Present}
    {SPEAR is a team dedicated to building a Mars rover every year, to send into various competitions. This year, our rover will be sent to the Canadian International Rover Challenge in Drumheller this August. My role is on the ECE team, where I've implemented things such as a CAN Bus software interface and an efficiently compressed video stream from the rover to the base station.}

%---------------------------------------------------------
\end{cventries}
